---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# sparseNumeric

<!-- badges: start -->
<!-- badges: end -->

The goal of sparseNumeric is to provide an S4 representation of sparse numeric vectors and a suite of arithmetic operations. A sparse vector stores only its non-zero entries and their positions, allowing efficient computation when most entries are zero.

## Installation

You can install the development version of sparseNumeric from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("anjieliu121/SDS375Homework5")
```

## Examples

### Initialization

Initialize a sparse vector directly

```{r example}
library(sparseNumeric)
v1 <- new("sparse_numeric",
value = c(3, 5),
pos = c(2L, 5L),
length = 6L)
v1
```

Convert a dense vector to a sparse vector

```{r}
dense <- c(0, 4, 0, 0, 7)
v2 <- as(dense, "sparse_numeric")

v2
```

Convert a sparse vector back to a dense vector

```{r}
as(v2, "numeric")
```

Display (show) a sparse vector

```{r}
v2
```

### Arithmetic Operations

Addition (generic + and sparse_add)

```{r}
x <- as(c(0, 1, 0, 2, 0), "sparse_numeric")
y <- as(c(3, 0, 0, 1, 4), "sparse_numeric")

x + y
sparse_add(x, y)
```

Subtraction (generic - and sparse_sub)

```{r}
x - y
sparse_sub(x, y)
```

Multiplication (generic * and sparse_mult)

```{r}
x * y
sparse_mult(x, y)
```

### Basic Operation

Count number of non-zero entries

```{r}
count_sparse(x)
```

### Advance Operations

Mean of a sparse vector

```{r}
mean(x)
```

Cross product

```{r}
sparse_crossprod(x, y)
```

Euclidean Norm

```{r}
norm(x)
```

Standardize a sparse vector

```{r}
standardize(x)
```

### Graphics

Plot overlapping non-zero elements of two sparse vectors


```{r, fig.alt = "Plot of overlapping non-zero elements of two sparse vectors"}
plot(x, y)
```